quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-17 paper-quollr.Rmd
Updated Figure 1 and 3

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.5, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.0259))

scurve_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a1", cex = 1)

scurve_proj_umap_model1_dp <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(0.2, 0, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 3,
  is_category = FALSE) +
  interior_annotation(label = "d", cex = 1)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.5, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.0259))

scurve_proj_umap_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a2", cex = 1)

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.5, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.031))

scurve_proj_umap_model3 <- plot_proj(
  proj_obj = proj_obj3,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a3", cex = 1)

@@

proj_obj4 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.5, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.031))

scurve_proj_umap_model4 <- plot_proj(
  proj_obj = proj_obj4,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a4", cex = 1) 
```

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            highd_data = scaled_limb_data, 
                            model_highd = scaled_limb_data_model, 
                            trimesh_data = trimesh_data_limb, 
                            axis_param = list(limits = 0.05,
                                              axis_scaled = 20, 
                                              axis_pos_x = -0.04, 
                                              axis_pos_y = -0.04, 
                                              threshold = 0.004))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            highd_data = scaled_limb_data, 
                            model_highd = scaled_limb_data_model, 
                            trimesh_data = trimesh_data_limb, 
                            axis_param = list(limits = 0.05,
                                              axis_scaled = 20, 
                                              axis_pos_x = -0.03, 
                                              axis_pos_y = -0.03, 
                                              threshold = 0.004))

>>>>

proj_obj1 <- get_projection(projection = projection, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.8, 
                                              axis_scaled = 3,
                                              axis_pos_x = -0.35, 
                                              axis_pos_y = -0.35, 
                                              threshold = 0.0623))

scurve_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-0.5, 0.55), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a1", cex = 1)

scurve_proj_umap_model1_dp <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(0.2, 0, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-0.5, 0.55), 
  axis_text_size = 3,
  is_category = FALSE) +
  interior_annotation(label = "d", cex = 1)

@@

proj_obj2 <- get_projection(projection = projection, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.6, 
                                              axis_scaled = 3,
                                              axis_pos_x = -0.35, 
                                              axis_pos_y = -0.35, 
                                              threshold = 0.05))

scurve_proj_umap_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-0.45, 0.4), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a2", cex = 1)

@@

proj_obj3 <- get_projection(projection = projection, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.5, 
                                              axis_scaled = 3,
                                              axis_pos_x = -0.34, 
                                              axis_pos_y = -0.34, 
                                              threshold = 0.0462))

scurve_proj_umap_model3 <- plot_proj(
  proj_obj = proj_obj3,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-0.43, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a3", cex = 1)

@@

proj_obj4 <- get_projection(projection = projection, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.6, 
                                              axis_scaled = 3,
                                              axis_pos_x = -0.35, 
                                              axis_pos_y = -0.35, 
                                              threshold = 0.048))

scurve_proj_umap_model4 <- plot_proj(
  proj_obj = proj_obj4,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-0.45, 0.46), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a4", cex = 1) 
```

@@

proj_obj1 <- get_projection(projection = projection, 
                            highd_data = scaled_limb_data, 
                            model_highd = scaled_limb_data_model, 
                            trimesh_data = trimesh_data_limb, 
                            axis_param = list(limits = 0.05,
                                              axis_scaled = 20, 
                                              axis_pos_x = -0.04, 
                                              axis_pos_y = -0.04, 
                                              threshold = 0.004))

@@

proj_obj2 <- get_projection(projection = projection, 
                            highd_data = scaled_limb_data, 
                            model_highd = scaled_limb_data_model, 
                            trimesh_data = trimesh_data_limb, 
                            axis_param = list(limits = 0.05,
                                              axis_scaled = 20, 
                                              axis_pos_x = -0.03, 
                                              axis_pos_y = -0.03, 
                                              threshold = 0.004))
